---
title: "How to use gnomesims"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to use gnomesims}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
## Purpose

The `gnomesims` package is designed to provide estimates of gene-environment correlation for simulated data. It is a tool for researchers who use polygenic scores of twins, parents and siblings to detect gene-environment correlation and want to address issues of power, sample size and effect size. We focus on two types of gene-environment correlation, namely, cultural transmission (= genetic nurture) and sibling interaction.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE
)
```

## Setup

The package can be installed from its' Github repository using `devtools`.

```{r warning=FALSE, results = "hide", message = FALSE}
# install.packages("devtools")
library(devtools)
devtools::install_github("josefinabernardo/gnomesims")
```

Next, it should be loaded it into you current session.

```{r setup}
library(gnomesims)
```

## Running a simulation using OpenMx

The core function of `gnomesims` is the `gnome_mx_simulation()` function. It takes in the ACE estimates, sample sizes, and effect size measures as arguments and returns two data frames with power estimates and path coefficients.

```{r warning=FALSE, message=FALSE}
gnome_mx_simulation(ct = .01, si = .025, npgsloci = 10)
```

Embedded within the simulation is the function `gnome_power()` to calculate power from alpha, degrees of freedom and the non-centrality parameter.

We recognize that the path coefficients are difficult to interpret. To solve this issue, the function `gnome_effect()` calculates a readily interpretable effect size measure.

## Running a simulation using generalized estimating equations

The package can also simulate results using generalized estimating equations (gee) with the `gnome_gee_simulation()` function. Functionality and results are similar to those of the `gnome_mx_simulation()` function.

```{r}
gnome_gee_simulation(ct = .01, si = .025, npgsloci = 10)
```


## In-built data sets

To demonstrate what type of data this package can generate, we have included two in-built data sets. They contain the results of the `gnome_mx_simulation()` function for 3 x 3 = 9 combination of AC covariance input parameters. The data set `gnome_power_data` contains the power results and the data set `gnome_params_data` contains parameter estimates.

```{r}
gnome_power_data
```

## Assortative mating

It is possible to look at results for present but unmodelled assortative mating by specifying the genotypic correlation between the parents. We are working on a version that estimates direct assortative mating when fitting the model.

```{r}
gnome_gee_simulation(ct = .01, si = .025, npgsloci = 10, assortm = .26)
```
