---
title: "How to use gnomesims"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{How to use gnomesims}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Purpose

The `gnomesims` package is designed to provide estimates of gene-environment correlation for simulated data. It is a tool for researchers who use polygenic scores of twins, parents and siblings to detect gene-environment correlation and want to address issues of power, sample size and effect size. We focus on two types of gene-environment correlation, namely, cultural transmission (=genetic nurture) and sibling interaction.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Setup

```{r setup}
library(gnomesims)
```

## Running a simulation using OpenMx

The core function of `gnomesims` is the `gnome_mx_simulation()` function. It takes in the ACE estimates, sample sizes, and effect size measures as arguments and returns two data frames with power estimates and path coefficients.

Embedded within the simulation is the function `gnome_power()` to calculate power from alpha, degrees of freedom and the non-centrality parameter.

We recognize that the path coefficients are difficult to interpret. To solve this issue, the function `gnome_effect()` calculates a readily interpretable effect size measure.
